Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/sections/Discussion.tex
Working on S3.

\vspace{3pt}\begin{lstlisting}
interface A { void m() {...} }
interface B extends A { void m() {...} }
interface C extends A { void m() {...} }
interface D extends B, C {}
\end{lstlisting}\vspace{3pt}
In the example, both $B.m$ and $C.m$ override $A.m$, so we think they should represent the same operation. In that case, we believe that D inherits
both conflicting methods without an explicit override, and it is in fact an intention conflict. Our calculus rejects these intentional conflicts by rule \textsc{(T-Intf)}, where $D$ is considered to be ill-formed. Nonetheless, as a general-purpose language, C++ accepts the definition of $D$, but forbids a cast from $D$ to $A$ because of ambiguity. For the conciseness of the proof, our language is more conservative on interfaces.
But we could also loosen the model and perform ambiguity check on casts and other expressions.

>>>>

\vspace{3pt}\begin{lstlisting}
interface A { void m() {...} }
interface B extends A { void m() {...} }
interface C extends A { void m() {...} }
interface D extends B, C {}
\end{lstlisting}\vspace{3pt}
In the example, both $B.m$ and $C.m$ override $A.m$, so we think they should represent the same operation. In that case, we believe that D inherits
both conflicting methods without an explicit override, and it is in fact an intention conflict. Our calculus rejects these intentional conflicts by rule \textsc{(T-Intf)}, where $D$ is considered to be ill-formed. Nonetheless, as a general-purpose language, C++ accepts the definition of $D$, but forbids a cast from $D$ to $A$ because of ambiguity. For the conciseness of the proof, our language is more conservative on interfaces, but open on up-casts. We could also loosen the model and perform ambiguity check on casts and other expressions. We need to handle more cases than C++, for instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$, it is still a diamond.

### 2017-10-09 NewVersion/sections/Formalization.tex
Working on S3.

\vspace{-2ex}
\subsection{Syntax}
The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
method implementations via default methods. This feature is 
closely related to \emph{traits}. To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
have method body, and in fact we are not introducing a different kind of methods, but they are just treated as normal methods that return empty. Abstract methods can be overridden with future implementations.

@@

Expressions can be standard constructs such as variables, method
invocation, or object creation. \name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of method invocation: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
implementation for method $m$ should be along the path $I$. 
% Another interesting expression are super-invocations, which enable a method to access an old implementation from the specified super type. Hence a super-invocation can only be used inside an interface definition.
Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
hence they are not supposed to appear in the source program. A value
``$\angl{I}\new{J}$''
is the final result of multiple reduction steps evaluating an
expression. Such value represents an object instance
of $J$ with an annotated static type $I$.

@@

Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
typing, well-formedness of methods and interfaces. As a convention, an environment
$\Gamma$ is maintained to store the types of variables, together with
the \kwthis type, namely
the enclosing type. 
% The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
% are very similar, in the sense that they all check the type of the specific method, by using
% an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
% illustrate later in Section~\ref{subsec:auxdefs}. After the method
% type is obtained, they all check that the arguments and the receiver
% have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
% path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

>>>>

\vspace{-2ex}
\subsection{Syntax}
The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
method implementations via default methods. This feature is 
closely related to \emph{traits}. To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
have method body, and in fact they can be considered as normal methods that return nothing. Abstract methods can be overridden with future implementations.

@@

Expressions can be standard constructs such as variables, method
invocation, or object creation, together with casts.
Again, to be concise, the casts are merely safe up-casts. Those cast-expressions
are in fact annotated expressions, where the annotation indicates its static type.
The coexistence of static and dynamic types is the key to hierarchical dispatch.
A value
``$(I)\new{J}$''
is the final result of multiple reduction steps evaluating an
expression.

@@

Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
typing, well-formedness of methods and interfaces. As a convention, an environment
$\Gamma$ is maintained to store the types of variables, together with
the self-reference $\kwthis$.
% The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
% are very similar, in the sense that they all check the type of the specific method, by using
% an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
% illustrate later in Section~\ref{subsec:auxdefs}. After the method
% type is obtained, they all check that the arguments and the receiver
% have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
% path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
